Constructing a universe for the setoid model

### 2020-10-13 paper.tex
Add full definition of inU and inU~

We will follow the method outlined in Section~\ref{ir-universes}. In
addition to $\inU$ for defining $\U$, we also introduce a family
$\inUU$ of binary relations between types in the universe, from which we
then define $\_\sim_{\setoidU}\_$.
\vspace{-0.2em}
\begin{align*}
  & \textsf{data}\ \inU : \mType \to \mType_1 \\
  & \textsf{data}\ \inUU : \{A\ A' : \mType\} \to \inU\ A \to \inU\ A' \to (A \to A' \to \mProp) \to \mType_1
\end{align*}

Just as the role of $\inU$ is, as before, to classify all types that are image
of $\El$, in the same way $\inUU\ p\ q$ classifies all relations of type $A \to
A' \to \mProp$ that are image of $\_\vdash\_\sim_{\El}\_$,
given proofs $p : \inU\ A, q : \inU\ A'$.
%
Note that $\inU$ appears in the sort of $\inUU$. Since these types are
mutually defined, they form an instance of \emph{induction-induction}, a schema
that allows the definition of a type mutually with other types that contain the
first one in their signature \cite{ii}.\footnote{The main example of
  induction-induction is the intrinsic definition of a dependent type theory in
  type theory \cite{tt-in-tt}.}

>>>>

We will follow the method outlined in Section~\ref{ir-universes}. In
addition to $\inU$ for defining $\U$, we also introduce a family
$\inUU$ of binary relations between types in the universe, from which we
then define $\_\sim_{\setoidU}\_$.
\vspace{-0.2em}
\begin{align*}
  & \textsf{data}\ \inU : \mType \to \mType_1 \\
  & \qquad \textsf{bool} : \inU\ \mathbbm{2} \\
  & \qquad \pi : \forall\{A\;A_\sim\;B\;B_\sim\}(a : \inU\;A)
  (b : (x : A) \to \inU\;(B\;x))\\
  & \qquad\ \to \inU\;a\;a\;A_\sim \to (\forall\{x_0\;x_1\}(x_{01} : A_\sim\;x_0\;x_1)
  \to \inUU\;(b\;x_0)\;(b\;x_1)\;(B_\sim\;x_{01})) \\
  & \qquad\ \to \inU\;
  (\Sigma\;(f : (x : A) \to B\;x) \\
  &\qquad\qquad\qquad\quad\, ((x_0\;x_1 : A)(x_{01} : A_\sim\;x_0\;x_1) \to B_\sim\;x_{01}\;(f\;x_0)\;(f\;x_1))) \\
  %%%%%%
  & \textsf{data}\ \inUU : \{A\ A' : \mType\} \to \inU\ A \to \inU\ A' \to (A \to A' \to \mProp) \to \mType_1 \\
  & \qquad \mathsf{bool}_\sim : \inUU\;\textsf{bool}\;\textsf{bool}\;
  (\lambda x_0\;x_1\; .\; x_0 \stackrel{?}{=}_{\mathbbm{2}} x_1) \\
  & \qquad \pi_\sim :
  \forall\{A_0\;A_1\;A_{0\sim}\;A_{01\sim}\;B_0\;B_1\;B_{0\sim}\;B_{1\sim}\;B_{01\sim}\}
  \{ a_0 : \inU\;A_0 \}\{ a_1 : \inU\;A_1 \}\\
  & \qquad\quad\quad\ \; \{b_0 : (x_0 : A_0) \to \inU\;(B_0\;x_0)\}
  \{b_1 : (x_1 : A_1) \to \inU\;(B_1\;x_1)\}\\
  & \qquad\quad\quad\ \; \{a_{0\sim} : \inUU\;a_0\;a_0\;A_{0\sim}\}
  \{a_{1\sim} : \inUU\;a_1\;a_1\;A_{1\sim}\} \\
  & \qquad\quad\quad\ \; \{ b_{0\sim} : \forall\{x_0\;x_1\}(x_{01} : A_{0\sim}\;x_0\;x_1)
    \to \inUU\;(b_0\;x_0)\;(b_0\;x_1)\;(B_{0\sim}\;x_{01}) \}\\
  & \qquad\quad\quad\ \; \{ b_{1\sim} : \forall\{x_0\;x_1\}(x_{01} : A_{1\sim}\;x_0\;x_1)
    \to \inUU\;(b_1\;x_0)\;(b_1\;x_1)\;(B_{1\sim}\;x_{01}) \}\\
  & \qquad\quad \to \inUU\;a_0\;a_1\;A_{01\sim} \\
    & \qquad\quad \to (\forall\{x_0\;x_1\}(x_{01} : A_{01\sim}\;x_0\;x_1)
      \to \inUU\;(b_0\;x_0)\;(b_1\;x_1)\;(B_{01\sim}\;x_{01})) \\
  & \qquad\quad \to \inUU\;(\pi\;a_0\;a_{0\sim}\;b_0\;b_{0\sim})\;
      (\pi\;a_1\;a_{1\sim}\;b_1\;b_{1\sim}) \\
  & \qquad\qquad\qquad\quad\,(\lambda f_0\;f_1\;.\;\forall(x_0\;x_1)\to A_{01\sim}\;x_0\;x_1
        \to B_{01\sim}\;x_{01}\;(\pi_1\;f_0\;x_0)\;(\pi_1\;f_1\;x_1))
\end{align*}

Just as the role of $\inU$ is, as before, to classify all types that are image
of $\El$, in the same way $\inUU\ p\ q$ classifies all relations of type $A \to
A' \to \mProp$ that are image of $\_\vdash\_\sim_{\El}\_$, given proofs $p :
\inU\ A, q : \inU\ A'$.
%
In particular, this definition of $\inUU$ states that the appropriate
equivalence for boolean elements is the obvious syntactic equality
$\_\stackrel{?}{=}_{\mathbbm{2}}\_$, whereas functions are to be compared
pointwise.
%
Note that $\inU$ appears in the sort of $\inUU$. Since these types are
mutually defined, they form an instance of \emph{induction-induction}, a schema
that allows the definition of a type mutually with other types that contain the
first one in their signature \cite{ii}.\footnote{The main example of
  induction-induction is the intrinsic definition of a dependent type theory in
  type theory \cite{tt-in-tt}.}
